%!TEX root=ndma.tex
This work is an attempt to provide a simple definition that merges the theories of nominal automata and $\omega$-regular languages, retaining effective closure under boolean operations, and decidability of emptiness, and language equivalence. We sketch some possible future directions. A very relevant application of formal verification in the presence of fresh resources could be model-checking of nominal process calculi. However, the presented theory only accommodates the deterministic case; undecidability issues arise for non-deterministic systems. Future work will be directed to identify (fragments of) nominal calculi that retain decidability. For this, one needs to limit not only non-determinism, but also parallel composition (again, decidability may be an issue otherwise). A calculus that could be handled by the current theory is a deterministic, finite-control variant of the $\pi$-calculus; capturing analogous versions of more recent calculi, e.g., $\psi$-calculi \cite{Bengtson11}, should be possible, as they are based on nominal structures with notions of permutation action, support, orbits. As mentioned in \autoref{sec:example}, we argue that deterministic behavior is enough to specify meaningful policies. 
%
Furthermore, recall that automata correspond to logic formulae: \hdmas{} could be used to represent logic formulae with binders; it would also be interesting to investigate the relation with first-order logic on nominal sets \cite{Bojanczyk13}. There may be different logical interpretations of \hdmas, where causality or dependence \cite{Vnnen07,Galliani12} between events are made explicit. Finally, extending the two-sorted coalgebraic representation of Muller automata introduced in \cite{CV12} to \hdmas{} would yield canonical representative of automata up to language equivalence.
